Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-10 paper.tex
Finished addressing the 1st reviewers notes and concerns.

\section{Faradaic Parameters}

With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we evaluate Faradaic conduction. The interface model uses two reverse connected diodes to reproduce the exponential behaviour of Faradaic current conduction, implied by the Butler-Volmer equation. We wish to measure this conduction by separating it from the displacement behaviour of the CPE. By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time. 
Like a conventional capacitor, when the voltage across the CPE changes, it responds by absorbing or ejecting charge, causing a spike in current. The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes. 
{\color{blue} In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.}
The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
\begin{equation}
    I = i_{0}  e^{V_{D} / n V_{T}}
\end{equation}
where $V_{T}$ is the thermal voltage and is approximately 25\thinspace mV at a temperature of 300\thinspace K. We wish to find how the saturation current ($i_{0}$) and the ideality factor ($n$) scale as the solution salinity is varied.

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes [TODO: Item 28] 2 and 6 whilst continuously measuring the output current. We commenced with 1.0X concentration of the stock solution (table~\ref{tab:PBSrecipe}). This solution was progressively diluted in factors of two between each measurement. The solution was mixed continuously using a standard laborotary grade magnetic stirrer. The solution was in equlibriumm with air prior to and during measurement and the electrodes remained submerged at all times.
A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

@@

In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements are plotted against time (solid lines). Each spike marks the point at which the voltage is incremented. We expect the peak current to be much higher than is shown since each measurement point is the average of 300 samples taken over 1 second. Note that the amount of charge absorbed by the CPE increases with concentration of PBS, but the current for each concentration converges to approximately the same value. Dotted lines have been added that link the electrical current measurements taken 10 seconds after each increment for 0.125X PBS (lower trace) and 1.0X PBS (upper trace). These dotted traces show results typical of cyclic methods, where the electrode overpotential is never constant. This illustrates the benefit of using DC measurements when measuring Faradaic currents.

@@

We attribute the change in behaviour between 0.9\thinspace V and 1.05\thinspace V to a transition to diffusion-controlled conduction.
We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk. It is this layer that is subsequently consumed by the Faradaic reactions at a rate dependent on the log of the electrode overpotential.  The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished. At this stage, and with increasing overpotential, the Faradaic conduction is governed by diffusion of ions from the bulk into the layer, the rate of which increases with the ion concentration in the bulk. We believe this explains the divergence of conduction with concentration between 0.9\thinspace V and 1.05\thinspace V and why there is no observable dependence on bulk ion concentration beforehand.

This hypothesis intimately links the Faradaic component to the CPE, where the latter is a precursor to the former. For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration. Further investigation into modelling this relationship is needed in order to extend the model into the diffusion controlled scenario. We hope to publish this in a follow-up paper.

@@

\begin{figure}
    \begin{center}
        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
    \end{center}
    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
    \label{fig:faradaic_currentVsVoltage}
\end{figure}

@@

Parameter values for $i_{0}$ and $n$ are presented in table~\ref{tab:FaradaicParams}. These parameters were found by fitting the diode equation to the results shown in figure~\ref{fig:faradaic_currentVsVoltage}.

\section{In-vivo measurements of sheep}

@@

    \bibitem{Mohtashami2011}
    Saba~Mohtashami,
    ``ELECTROCHEMICAL PROPERTIES OF FLEXIBLE ELECTRODES FOR IMPLANTED NEUROMUSCULAR EXCITATION APPLICATIONS'',
    Open Acess Dissertations and Theses (2011), Paper 6152

@@

{\color{blue}
I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding. On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
{\color{OliveGreen}
    Item 1\\
    {\color{Red} Research textbook knowledge and published state of the art relating to electro chemistry in our area.}
    This response has concerned us and we have subsequently invested considerable effort in broadening our search of published state-of-the-art. Where possible we have included references to electrochemistry literature from any areas we are dealing with in this revision. During this expansion we were unable to find anything that subtracts from the novelty of this work. That said, our work is concerned primarily with the electrical side of an interface impedance and more specifically with that of an implanted electrode. Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in a purely mathematical construct, regardless of the chemistry at play.
}\\

1. The interface model as such is not new and has been published extensively.\\
{\color{OliveGreen}
    Item 2\\
    {\color{Red} Review and discuss existing interface models}
    No response yet.
}\\

2. The authors do not at all comment on interface polarization, which is particularly important under DC conditions. As soon as an electrode carries current, such phenomena become important and relevant.\\
{\color{OliveGreen}
    Item 3\\
    {\color{Red} Is polarisation a separate mechanism from double layer formation? If so, can we address? Polarisation will be just as important in cyclic measurement techniques where the cycle time is low. Does anyone understand polarisation sufficiently to remove it from measurements? Is polarisation not just remaining charge in a layer around an electrode, is it not just the double layer?}
    No response yet.
}\\

3. To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones. This is particularly relevant for the measurements in Fig. 3 and the related and subsequent text.\\
{\color{OliveGreen} 
    Item 4\\
    {\color{Red} I don't understand what use doing this would be. All voltage dropped between two end electrodes, voltage proportional to total impedance between electrodes. The most use you could get from this would be to find how much is dropped across a single interface, which is exactly what we are doing.}
    No response yet.    
}\\

4. The authors never mention the origin of any Faradaic contribution at the electrodes. What is the electro- or redox-chemistry that the authors assume to happen?? Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
{\color{OliveGreen}
    Item 5\\
    {\color{Red} Do we wish to get into this? Perhaps we could touch on it (after reviewing electrochemistry literature) but leave it loose and mention that it is not our intention to completely understand the mechanisims at the chemical level, rather to compare an available model with measurements and comment.}
    No response yet.
}\\

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    Item 6\\
    {\color{Red} Enhance color variation in Figures 4 and 5 and make a reference to Figure 5}
    Graphs redrawn with a wider range of shading to help identify traces.
}\\

6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
{\color{OliveGreen}
    Item 7\\
    {\color{Red} The diodes are identical, this is moving into polarisation territory again. In effect, they are both being used (one by + and other by -). I don't know what to say about this. We wanted to make all the measurements happen in as little time as possible. We have data from sweeps in the other direction, not DC though.}
    No response yet.
}\\

7. There is a big difference between blue dots and red curve in Fig. 10, except for the "voltage increment time" and "64 seconds after increment".  This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
{\color{OliveGreen}
    Item 8\\
    {\color{Red} This is true, try and pinpoint exactly why this is happening. Why does the CPE perform so well in the CPE frequency response plots yet so poorly in the Faradaic part?}
    No response yet.
}\\
}

@@

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    {\color{Red} Estimate current density and investigate possible effects}
    Have added a new figure to show the current density during CPE measurement.
}

In addition,  measurement apparatus information is fully lacking.\\
{\color{OliveGreen}
    Item 11\\
    {\color{Red} Describe instruments used in measurements or make reference to Jonathans paper}
    Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified thier reuse for displacement measurements.
}\\

@@

1. You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14). I want to know how much charge was being applied to these electrodes at low frequencies (e.g. 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
{\color{OliveGreen}
    Item 18\\
    {\color{Red} Estimate the amount of charge being injected in each of the measurements (fits with the current density)}
    Instrumentation for CPE measurements have been added. I have also added current density and peak stimulus voltage information to displacement current measurement. [TODO: Calculate and add total charge transfer for both CPE and Faradaic].
}\\

@@

1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
{\color{OliveGreen}
    Item 20\\
    {\color{Red} Replace ``A 0.1X concentration'' with ``a one-tenth concentration...'' and explain exactly what that means.}
    Yes, thank you, see amendment.
}\\

@@

4. In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE. But surely it is not since the sloping lines become horizontal. It is the CPE in series with something. But what is this something? Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
{\color{OliveGreen}
    Item 23\\
    {\color{Red} Reword the caption of Fig. 4 to include the series resistance.}
    Thank you, have reworded the caption in Figure 4 to more accuratly describe the situation.
}\\

@@

10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
{\color{OliveGreen} 
    Item 29\\
    {\color{Red} What I originally thought, I don't know where inductive stirrer came from}
    Changed mention of inductive stirrer to magnetic stirrer.
}\\

11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
{\color{OliveGreen} 
    Item 30\\
    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
    Removed reference to the CPE element and have better quantified the settling period in that footnote.
}\\

12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
{\color{OliveGreen}
    Item 31\\
    {\color{Red} Yes, this is better. Replace with this.}
    Yes, that is better - thank you.
}\\

13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
{\color{OliveGreen}
    Item 32\\
    {\color{Red} Correct, maybe a diargam of the hypothesis is required - nobody seemed to dispute the hypothesis. Check there is no ``textbook knowledge'' explanation for this beforehand.}
    Changed references to the CPE model element in the conclusion to the electrical double layer.
}\\

>>>>

\section{Faradaic Parameters}
{
    \color{blue}
    Our model uses two reverse connected diodes to represent Faradaic current conduction between electrode and electrolyte. Specifically we use the diodes to model irreversible Faradaic reactions. Any reversible reactions, those producing reactants bound to the surface of the electrode, are encapsulated by the displacement branch (CPE) of the model.
    Possible irreversible Faradaic reactions for platinum electrodes in saline are:
    \begin{eqnarray}
        Pt + 4Cl^{-} &\Rightarrow& [PtCl_{4}]^{2-} + 2 e^{-}\\
        2H_{2}O + 2 e^{-} &\Rightarrow& H_{2}\uparrow + 2OH^{-}\\
        2H_{2}O &\Rightarrow& O_{2}\uparrow + 4H^{+} + 4e^{-}\\
        2Cl^{-} &\Rightarrow& Cl_{2}\uparrow + 2e^{-}\\
        Cl^{-} + H_{2}O &\Rightarrow& ClO^{-} + 2H^{+} + 2e^{-}
    \end{eqnarray} 
}
With parameters fitted for the scaling of both the CPE and $R_{S}$ with PBS concentration, we evaluate Faradaic conduction. The interface model uses two reverse connected diodes to reproduce the exponential behaviour of Faradaic current conduction, implied by the Butler-Volmer equation. We wish to measure this conduction by separating it from the displacement behaviour of the CPE. By using a DC measurement technique, as opposed to cyclic measurements, we are able to separate the effects in time. 
Like a conventional capacitor, when the voltage across the CPE changes, it responds by absorbing or ejecting charge, causing a spike in current. The CPE will draw negligible current once it has settled and in the case of our model we assume the remaining current conduction to be the result of Faradaic processes. 
{\color{blue} In \cite{Greatbatch1969} it is shown that the stirring of an air-saturated solution of physiological saline reduces the settling time of platinum electrodes to stimulus transients; with both situations eventually settling to the same impedance.}
The equation governing current conduction in a diode where the forward voltage across the diode, $V_{D}$, is small is
\begin{equation}
    I = i_{0}  e^{V_{D} / n V_{T}}
\end{equation}
where $V_{T}$ is the thermal voltage and is approximately 25\thinspace mV at a temperature of 300\thinspace K. We wish to find how the saturation current ($i_{0}$) and the ideality factor ($n$) scale as the solution salinity is varied.

Faradaic measurements were made using an Agilent E5270B Precision Measurement Mainframe producing a stepped DC voltage stimulus across electrodes 3 and 7 whilst continuously measuring the output current. 
{
    \color{blue}
    The use of electrodes 3 and 7 was made because the connection to electrode 2 in our Octrode had been damaged. This alteration has no impact on the validity of results as all other electrodes are left to float.
}

Measurements commenced with a 4.5 litre solution of 1.0X PBS which was progressively diluted in factors of two between each measurement. The solution was mixed continuously using a standard laboratory grade magnetic stirrer. The solution was in equilibrium with air prior to and during measurement and the electrodes remained submerged at all times.
A single measurement run involved stepping the voltage across electrodes 2 and 7 from 0.5\thinspace V to 1.2\thinspace V in increments of 0.05\thinspace V; this range was previously determined to capture the onset of Faradaic conduction.

@@

In figure~\ref{fig:StepResponse_Faradaic}, electrical current measurements are plotted against time (solid lines). Each spike marks the point at which the voltage is incremented by 50\thinspace mV. Note that the amount of charge absorbed by the CPE increases with concentration of PBS, but the current for each concentration converges to approximately the same value. Dotted lines have been added that link the electrical current measurements taken 10 seconds after each increment for 0.125X PBS (lower trace) and 1.0X PBS (upper trace). These dotted traces show results typical of cyclic methods, where the electrode overpotential is never constant. This illustrates the benefit of using DC measurements when measuring Faradaic currents.

@@

@@

%\begin{figure}
%    \begin{center}
%        \includegraphics{graphics/faradaic_currentVsVoltageIEEE}
%    \end{center}
%    \caption{Simulated response of the interface model compared to measurement from the electrodes with a stepped voltage overpotential. Measurement points show current values taken at the $64^{th}$ second after each voltage increment.}
%    \label{fig:faradaic_currentVsVoltage}
%\end{figure}

@@

%Parameter values for $i_{0}$ and $n$ are presented in table~\ref{tab:FaradaicParams}. These parameters were found by fitting the diode equation to the results shown in figure~\ref{fig:faradaic_currentVsVoltage}.

We attribute the change in behaviour between 0.9\thinspace V and 1.05\thinspace V to a transition to diffusion-controlled conduction.
We hypothesise that the charging of the CPE draws available ions to the electrode, creating a layer of high ionic concentration at the surface irrespective of that of the solution bulk. It is this layer that is subsequently consumed by the Faradaic reactions at a rate dependent on the log of the electrode overpotential.  The effect of bulk solution concentration while this layer has formed is negligible until the point at which the layer is consumed faster than it can be replenished. At this stage, and with increasing overpotential, the Faradaic conduction is governed by diffusion of ions from the bulk into the layer, the rate of which increases with the ion concentration in the bulk. We believe this explains the divergence of conduction with concentration between 0.9\thinspace V and 1.05\thinspace V and why there is no observable dependence on bulk ion concentration beforehand.
For the purposes of our model, we are content with placing a limit of 0.9\thinspace V across the pair of interfaces and using the assumption that Faradaic conduction does not change with concentration.

{
    \color{blue}
Figure~\ref{fig:faradaic_currentVsTime} shows a subset of the data used in Fig.~\ref{fig:StepResponse_Faradaic} (the 1.0X PBS trace) to show the fit between simulated and measured data. Here the simulation contains fitted diode parameters, shown in table~\ref{tab:FaradaicParams}, which give rise to the exponentially increasing steady state current.
It is apparent from this trace that the temporal response of the CPE does not match the transient decay curves seen in the Faradaic measurements, something the CPE should predict. These transient decay curves appear to have time-constant that decreases with each subsequent measurement. This variable time-constant phenomena is especially clear when looking back at figure~\ref{fig:CPE_currentVsTime}. Although the Faradaic response transients appear to approach the time-constant predicted by the CPE, there is clearly behaviour not completely described by the CPE.

We hope to extend this model into a diffusion controlled conduction scenario and extend the CPE element to mimic the variable time-constant behaviour in a follow up paper.
}
\section{In-vivo measurements of sheep}

@@

    \bibitem{Mohtashami2011}
    Saba~Mohtashami,
    ``Electrochemical Properties of Flexible Electrodes for Implanted Neuromuscular Excitation Applications'',
    Open Acess Dissertations and Theses (2011), Paper 6152

@@

{\color{blue}
I am not very enthusiastic about his paper as it does not contain many novel or original ideas and finding. On the electrochemistry side it is superficial and falls back behind published state of the art and textbook knowledge.\\
{\color{OliveGreen}
    Item 1\\
    This response has concerned us and we have subsequently invested considerable effort in broadening our search of published state-of-the-art. Where possible we have included references to electrochemistry literature from any areas we are dealing with in this revision. During this expansion we were unable to find anything that subtracts from the novelty of this work. That said, our work is concerned primarily with the electrical side of an interface impedance and more specifically with that of an implanted electrode. Our intention is to be able to encapsulate the electrical aspect of the interface and surrounding electrolyte in an equivalent electrical circuit, regardless of the chemistry at play.
}\\

1. The interface model as such is not new and has been published extensively.\\
{\color{OliveGreen}
    Item 2\\
    Correct, there are many published interfacial models. This model differentiates itself from those by being compact. Compact in the sense that it can be entered into any common electronic circuit simulator and used to make predictions about impedance. This is especially important for elecronic engineers designing medical impalant devices.
}\\

2. The authors do not at all comment on interface polarization, which is particularly important under DC conditions. As soon as an electrode carries current, such phenomena become important and relevant.\\
{\color{OliveGreen}
    Item 3\\
    We have lumped the effects of polarisation into the response of the displacement element in the model (CPE). The introduction to the Displacement Parameters section has been updated to include mention of polarisation. Our technique for measuring Faradaic reactions, namely to apply a DC voltage and wait until current transients settle before making a measurement, has been choosen to minimise any contribution from polarisation effects.
}\\

3. To assess the resistivity or impedance of a material between two electrodes, one normally uses a 4-electrode setup with injection of current through the two outer electrodes, while measuring a voltage between the inner ones. This is particularly relevant for the measurements in Fig. 3 and the related and subsequent text.\\
{\color{OliveGreen} 
    Item 4\\
    We are not so much interested in knowing the resistivity of the solution as we are in knowing the resistance between any pair of electrodes for the specific electrode array. The difference being that we expect the geometry of the electrode array, being comprised of 8 cylindrical coaxially placed electrodes as shown in Fig.~1, to determine the resistance in a non-trivial way. Using the transimedance measurements we can construct a mesh that represents the geometry of the electrodes and the resistivity of the solution. Another benefit in the method chosen is that it does not rely on knowing the electrode geometry and is therefore more versatile.
}\\

4. The authors never mention the origin of any Faradaic contribution at the electrodes. What is the electro- or redox-chemistry that the authors assume to happen?? Gas formation at the electrodes, electrolysis of the saline, i.e., hydrogen and oxygen formation??\\
{\color{OliveGreen}
    Item 5\\
    Relevant Faradaic reactions, both reversible and irreversible, have been added both to the displacement/polarisation and Faradaic sections.
}\\

5. Figure 5 is not referenced anywhere in the text. Also the blue variations in the curves are hardly visible.\\
{\color{OliveGreen} 
    Item 6\\
    Graphs redrawn with a wider range of shading to help identify traces and referenced on page 3 (now figure \ref{fig:CPE_Phase}).
}\\

6. Since the electrode model includes two back-to-back diodes, I think it would be valuable to sweep the voltage from -1.2V to +1.2V.\\
{\color{OliveGreen}
    Item 7\\
    The measurements involving the back-to-back diodes are those measuring the contribution from irreversible Faradaic reactions. These measurements involve two active electrodes while the remaining electrodes and the electrolyte have a floating potentials. Sweeping the voltage from -1.2V to +1.2V in this case would be the equivalent of swapping the terminals halfway through the sweep. Physically this would not be the same as polarisation effects would linger, however we are only interested in the steady state Faradaic conduction where we assume polarisation and displacement effects are negligible.
}\\

7. There is a big difference between blue dots and red curve in Fig. 10, except for the "voltage increment time" and "64 seconds after increment".  This indicates to me that the CPE model is NOT that accurate, as the settling curve is highly correlated to the CPE parameters.\\
{\color{OliveGreen}
    Item 8\\
    We have addressed this discrepancy on page 5. The frequency response of the CPE is still valid, which is what we had fitted the parameters. We agree that the time-domain response of the CPE may need further work. Thank you for your time and critique. 
}\\
}

@@

page 2 Measurement of the CPE. What was the current density used in EIS measurements?
What is the effect of chosen current density on CPE impedance (Fig. 5)?
{\color{OliveGreen}
    Item 10\\
    Added a new figure to show the current density during CPE measurement.
}

In addition,  measurement apparatus information is fully lacking.\\
{\color{OliveGreen}
    Item 11\\
    Added missing details of instrumentation used to conduct inter-electrode resistance measurements and clarified their reuse for displacement measurements.
}\\

@@

1. You do not explain how the impedance measurements have been made (Figs 4, 5 13 & 14). I want to know how much charge was being applied to these electrodes at low frequencies (e.g. 0.05 Hz): what potential excursion occurred was it really a ``small signal''?\\
{\color{OliveGreen}
    Item 18\\
    Instrumentation for CPE measurements have been added. I have also added current density and peak stimulus voltage information to displacement current measurement. [TODO: Calculate and add total charge transfer for both CPE and Faradaic].
}\\

@@

1. P1, top RH col. ``0.1X'' ought to be explained when you first use this form.\\
{\color{OliveGreen}
    Item 20\\
    Yes, thank you, see amendment.
}\\

@@

4. In the legend of Fig 4 and in paragraph below, you say this is magnitude of the CPE. But surely it is not since the sloping lines become horizontal. It is the CPE in series with something. But what is this something? Is it the total series resistance or have you already subtracted the volume resistance (found in section II)?\\
{\color{OliveGreen}
    Item 23\\
    Thank you, have reworded the caption in Figure 4 to more accurately describe the situation.
}\\

@@

10. P3, col 2, line 36. I guess you mean what is usually called a Magnetic Stirrer. Not ``inductive'' surely?\\
{\color{OliveGreen} 
    Item 29\\
    Changed mention of inductive stirrer to magnetic stirrer.
}\\

11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
{\color{OliveGreen} 
    Item 30\\
    Removed reference to the CPE element and have better quantified the settling period in that footnote.
}\\

12. Fig 11 legend ``Simulated and measured response of the interface model''. Surely you mean ``Simulated response of the interface model compared to measurement from the electrodes''?\\
{\color{OliveGreen}
    Item 31\\
    Yes, that is better - thank you.
}\\

13. P5, col 2, line 46 ``the CPE is setting''. Again, you are confusing an element of your model with reality.\\
{\color{OliveGreen}
    Item 32\\
    Changed references to the CPE model element in the conclusion to the electrical double layer.
}\\
